|

### 2022-04-07 01-Chp-Background.Rmd
Fixed missing short caption for a table
Final corrections

[While widely used in the published literature, the validity of these dementia subtypes as distinct clinical outcomes is debatable.]{.correction} Vascular dementia regularly co-occurs in patients with Alzheimer's disease,[@iadecola2013] [a]{.correction} presentation described as "mixed" dementia.[@custodio2017] [Evidence from autopsies performed as part of longitudinal population based samples, such as the Medical Research Council Cognitive Function and Ageing Study,]{.correction}[@chadwick1992] [found that a majority of participants had evidence of both Alzheimer's disease and vascular pathology.]{.correction} [@neuropathologygroupofthemedicalresearchcouncilcognitivefunctionandageingstudymrccfas2001] [This suggests that the "pure" clinical subtypes of dementia are less common than the "mixed" outcome, particularly in older age groups,]{.correction}[@schneider2007] [and indicates that a composite all-cause dementia outcome might be considered more analytically valid than outcomes based on a single dementia subtype.]{.correction}

@@

[Additionally, multimorbidity is common among people with dementia, with those diagnosed frequently having two or more other chronic conditions,]{.correction}[@poblador-plou2014] [including diabetes, depression and cerebrovascular disease.]{.correction}[@bauer2014] [Dementia makes the diagnoses and management of comordid conditions harder, as people living with dementia may not be in a position to seek primary care]{.correction}[@cooper2017] [or self-manage treatments.]{.correction}[@sinclair2000]

@@

Given the substantial burden that dementia represents and the absence of any curative therapies, as detailed in the above sections, the assessment of easily modifiable targets for their utility in the prevention of dementia should be prioritized.[@winblad2016] [Previously-examined risk factors for the condition include cardiovascular factors (e.g. hypertension), education, diabetes, and smoking.]{.correction}[@anstey2019] The benefits of a prevention-based approach based on addressing known risk factors for dementia are well-studied. Reducing the prevalence of the seven most important risk factors for dementia (obesity, hypertension, diabetes, smoking, physical inactivity, [depression,]{.correction} and low educational attainment) by 10-20% per decade is estimated to result in a reduction in dementia prevalence of 8-15% by 2050.[@norton2014potential]

@@

@@

[A final general limitation of studies of statin use is their limited ability to assess a causal link between lipid levels and dementia. This is caused by the pleiotropic effect of statins, which may effect dementia risk via some non-lipid-lowering pathway. For example, statins influence the levels of C-reactive protein,]{.correction}[@albert2001] [an independent risk factor for dementia.]{.correction}[@lewis2021; @schmidt2002]

@@

Recent MR studies indicated that genetically determined low levels of LDL-c may cause a reduction in AD risk.[@larsson2017; @ostergaard2015] However, the effect was attenuated in sensitivity analyses that exclude the region surrounding the _Apo_$\mathcal{E}$ gene, the strongest known risk factor for Alzheimer's disease.[@kim2009] Inclusion of _Apo_$\mathcal{E}$ variants invalidates the exclusion restriction criteria [of MR analyses], as the risk reduction observed may be driven by variants in this region via a pathway independent of lipid levels. This was supported by further MR studies in which the observed effect attenuated to the null after _Apo_$\mathcal{E}$ variants were excluded.[@benn2017] Despite the increasing number of MR studies examining this topic, no systematic review of this study design as a source of evidence has been performed.

>>>>

[While widely used in the published literature, the validity of these dementia subtypes as distinct clinical outcomes is debatable.]{.correction} Vascular dementia regularly co-occurs in patients with Alzheimer's disease,[@iadecola2013] [a]{.correction} presentation described as "mixed" dementia.[@custodio2017] [Evidence from autopsies performed as part of longitudinal population based samples, such as the Medical Research Council Cognitive Function and Ageing Study,]{.correction}[@chadwick1992] [found that a majority of participants had evidence of both Alzheimer's disease and vascular pathology.]{.correction} [@neuropathologygroupofthemedicalresearchcouncilcognitivefunctionandageingstudymrccfas2001] [This suggests that the "pure" clinical subtypes of dementia are less common than the "mixed" outcome, particularly in older age groups,]{.correction}[@schneider2007] [and indicates that a composite "all-cause" dementia outcome may be more analytically valid than outcomes based on a single dementia subtype.]{.correction}

@@

[Additionally, multimorbidity is common among people with dementia, with patients frequently having two or more other chronic conditions,]{.correction}[@poblador-plou2014] [including diabetes, depression and cerebrovascular disease.]{.correction}[@bauer2014] [Dementia makes the diagnoses and management of comordid conditions harder, as people living with dementia may not be in a position to seek primary care]{.correction}[@cooper2017] [or self-manage treatments.]{.correction}[@sinclair2000]

@@

Given the substantial burden that dementia represents and the absence of any curative therapies, as detailed in the above sections, the assessment of easily modifiable targets for their utility in the prevention of dementia should be prioritized.[@winblad2016] [Previously-examined risk factors for the condition include cardiovascular factors (e.g. hypertension), education, diabetes, and smoking.]{.correction}[@anstey2019] [Similarly,]{.correction} the benefits of a prevention-based approach based on addressing known risk factors for dementia are well-studied. Reducing the prevalence of the seven most important risk factors for dementia (obesity, hypertension, diabetes, smoking, physical inactivity, [depression,]{.correction} and low educational attainment) by 10-20% per decade is estimated to result in a reduction in dementia prevalence of 8-15% by 2050.[@norton2014potential]

@@

(ref:lipidTreatments-scaption) Summary of available treatments for hyperlipidaemia.

@@

[A final general issue with studies of statin use is their limited ability to assess a causal link between lipid levels and dementia. This is due to the potential pleiotropic effects of statins, which may effect dementia risk via some non-lipid-lowering pathway. For example, previous work has shown that statins influence the levels of C-reactive protein,]{.correction}[@albert2001] [an independent risk factor for dementia.]{.correction}[@lewis2021; @schmidt2002]

@@

Recent MR studies indicated that genetically determined low levels of LDL-c may cause a reduction in AD risk.[@larsson2017; @ostergaard2015] However, the effect was attenuated in sensitivity analyses that exclude the region surrounding the _Apo_$\mathcal{E}$ gene, the strongest known risk factor for Alzheimer's disease.[@kim2009] Inclusion of _Apo_$\mathcal{E}$ variants invalidates the exclusion restriction criteria [of MR analyses]{.correction}, as the risk reduction observed may be driven by variants in this region via a pathway independent of lipid levels. This was supported by further MR studies in which the observed effect attenuated to the null after _Apo_$\mathcal{E}$ variants were excluded.[@benn2017] Despite the increasing number of MR studies examining this topic, no systematic review of this study design as a source of evidence has been performed.

### 2022-04-07 05-Chp-CPRD-Analysis.Rmd
Final corrections

This finding disagrees with the results of the original analysis [reported by Smeet _et al_,]{.correction} [@smeeth2009] which found evidence for a protective effect of statin use on all-cause dementia (`r estimate(0.81, 0.69,0.96,type = "HR")`) and non-AD dementia (`r estimate(0.82,0.69, 0.97,type = "HR")`), but little evidence of an effect on AD (`r estimate(0.81,0.49, 1.35, type="HR")`).

>>>>

This finding disagrees with the results of the original analysis [reported by Smeeth _et al_,]{.correction} [@smeeth2009] which found evidence for a protective effect of statin use on all-cause dementia (`r estimate(0.81, 0.69,0.96,type = "HR")`) and non-AD dementia (`r estimate(0.82,0.69, 0.97,type = "HR")`), but little evidence of an effect on AD (`r estimate(0.81,0.49, 1.35, type="HR")`).

### 2022-04-07 08-Discussion.Rmd
Final corrections

[Fourthly, despite their wide use in the existing literature (as illustrated in the systematic review in Chapters]{.correction} \@ref(sys-rev-methods-heading) [&]{.correction} \@ref(sys-rev-results-heading) [), the clinical validity of dementia subtypes could be questioned and may lead to spurious results. This is supported by the difficulty in diagnosing a specific dementia subtype, and findings from population-based autopsies samples suggesting that "pure" Alzheimer's/vascular dementia outcomes are rare when compared to "mixed" dementia outcomes in older age groups, as discussed in detail in the Introduction (see Section]{.correction} \@ref(underlying-pathologies)[). In this case, results for the all-cause dementia outcome may be the most clinically useful, but were not the focus of the final chapters of these thesis.]{.correction}

>>>>

[Fourthly, despite their wide use in the existing literature (as illustrated in the systematic review in Chapters]{.correction} \@ref(sys-rev-methods-heading) [&]{.correction} \@ref(sys-rev-results-heading) [), the clinical validity of dementia subtypes (Alzheimer's disease, vascular dementia, etc.) could be questioned and may lead to spurious results. This is supported by the difficulty in diagnosing a specific dementia subtype, and findings from population-based autopsies samples suggesting that "pure" Alzheimer's/vascular dementia outcomes are rare when compared to "mixed" dementia outcomes in older age groups, as discussed in detail in the Introduction (see Section]{.correction} \@ref(underlying-pathologies)[). In this case, results for the all-cause dementia outcome may be the most clinically useful, but this outcome was not the primary focus of the final chapters of these thesis.]{.correction}
